Outline flowCore paper

### 2008-01-16 paper/outline.tex
I start to add text to the introduction and different section.
git-svn-id: file:///home/git/hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/flowCore@29548 bc3139a8-67e5-0310-9ffc-ced21a209358

\subsection{High throughput flow}
A brief introduction to the flow technology and high throughput flow
in particular.

{\bf RB:} Given the proposed journal, an introduction to flow technology isn't
required.

\subsection{R and Bioconductor}
A couple of sentences what Bioconductor and R is all
about.

@@

@@

\subsection{demands on flow data structures}
numeric raw data matrices
instrument-specific meta data
experiment meta data
memory issues, scale of data (tubes, plates)

\subsection{flowFrame}
to represent individual FCS files

@@

\subsection{transformations}
Different flavors, R's own transformation infrastructure allows for
arbitrary transforms

>>>>

%%\subsection{High throughput flow}
A brief introduction to the flow technology and high throughput flow
in particular.
{\bf RB:} Given the proposed journal, an introduction to flow technology isn't
required.

\textit{introduction or abstract (first draft)} \\

Traditionally, flow cytometry has been a tube-based technique limited
to small-scale laboratory and clinical studies.  High throughput
methods for flow cytometry have recently been developed and are now
used in both basic and clinical research. Today, the need for flexible
and well structured informatic tools to efficiently handle and analyze
FC-HCS has considerably increased. Indeed, the amount of information
generated by these technology must be stored, managed, and needs to be
summarized in order to be accessible to the researcher. However, the
absence of any research platform which bioinformaticians, computer
scientists, and statisticians can use to develop standard or novel
methods for flow cytometric has become problematic. We believe that
the Open Source statistical software R in conjuction with the
Bioconductor Project can fill this gap.  In this paper, we propose R
data structures to handle flow cytometry data through the main steps
of importing, storing, assessing and preprocessing data from FCM
experiments. These methods, along with a number of specialized
functions for compensation, transformation and filtering preprocessing
steps, are implemented in the new developped Bioconductor package
flowCore.  The aim is that researchers will find flowCore to be a
solid foundation for efficiently handling FC-HCS data and for future
development of new methods and tools for the analysis of flow
cytometry.

\textit{end --- introduction (first draft)}

\subsection{R and Bioconductor}

R is a solid statistical framework/environment, particularly desirable
when analyzing the large numeric datasets arising from High throughput
experiments such as FC-HCS. Indeed, this open source software already
offer lots of statistical and visualization methods developpement for
various field of application but potentially interesting for FC-HCS
data analysis. R is also a research platform which bioinformaticians,
computer scientists, and statisticians can use to develop new methods
for FC-HCS. In biolgy the Bioconductor project....

@@

\textit{example Text}

\Rpackage{flowCore}'s primary task is the representation and basic
manipulation of flow cytometry (or similar) data. This is accomplished
through a data model very similar to that adopted by other
Bioconductor packages used for gene expression analysis and thus
familiar to most Bioconductor users \cite{}.  The data structure is
designed to combine several differents sources of information into a
single convenient structure: (\textit{e.g.,} measurements from a
combination of samples, metadata describing samples in the
experiments).

\textit{end Text}

@@

\subsection{demands on flow data structures}

numeric raw data matrices
instrument-specific meta data
experiment meta data
memory issues, scale of data (tubes, plates)

\subsection{flowFrame}

\textit{example Text}

The basic unit of manipulation in \Rpackage{flowCore} is the
\Rclass{flowFrame}, which corresponds roughly with a single ``FCS''
file exported from the flow cytometer's acquisition software. The
\Robject{flowFrame} object store the event-level information and the
parameters, which contain metadata. The event information, stored as a
single matrix, is easily accessed and manipulated (see
\textit{Supplementary Materials}). The parameters slot contains
information derived from an FCS file's ``\$P<n>'' keywords, which
describe the detector and stain information.

\textit{end Text}

{\bf NLM:} Should be more abstract ?

to represent individual FCS files

@@

\subsection{transformations}
Different flavors, R's own transformation infrastructure allows for
arbitrary transforms, we have implemented the commonly used one.
